---
title: "RNAseq Report"
fontsize: 12pt
doumentclass: article
classoption: letterpaper
geometry: margin=0.5in
output: 
    pdf_document:
        fig_width: 7.5
        fig_height: 5
        fig_caption: false
        fig_crop: false
        dev: cairo_pdf
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
HOME = "/home/ubuntu"
source(file.path(HOME, "dev/rnaseqr/R/functions.R"))
library(configr)
config = read.config(file = "/home/ubuntu/dev/rnaseqr/config.toml")
project = config$output$project
load(file.path(project, "deg.RData"))
```

This DEG analysis was run with the following configuration:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
config
```


```{r}
dim(counts)
rownames(counts)[1:10]
colnames(counts)[1:10]
```

\pagebreak

## Clustered heatmap of raw counts scaled by gene

The following heatmap shows your `r ncol(counts)` samples clustered by the expression profiles
of the `r config$plotting$heatmap$n_top_variable_genes` genes that exhibit the largest variance 
across the dataset. Values in heatmap cells are raw counts that have been scaled gene-wise (i.e.,
row-wise).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
pretty_draw_hm(counts,
               genes = top_n_variable_genes(counts, 100),
               column_names_gp = gpar(fontsize = 8))
```

\pagebreak
## Principle component reduction of expression profiles

The following PCA is based on the expression profiles of the top `r config$plotting$pca$n_top_variable_genes` 
genes (again in tersm of rowwise variance) present in the filtered dataset.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
PC1_varExpl = {round(attributes(pca_pltdata)$percentVar[1]*100, 2)}
PC2_varExpl = {round(attributes(pca_pltdata)$percentVar[2]*100, 2)}
ggplot(pca_pltdata, aes(x=PC1, y = PC2, color = treatment)) +
  geom_point(size = 6) +
  geom_text(aes(label = sample), color = "black", size = 4) +
  xlab(glue::glue("PC1 ({PC1_varExpl}%)")) +
  ylab(glue::glue("PC2 ({PC2_varExpl}%)")) +
  theme_bw() +
  theme(
        panel.grid = element_blank()
        )
```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_volcano(results[[1]],
             group1 = "BHB",
             group2 = "control",
             return_figs = TRUE,
             n_label = 20,
             lfccut = config$deg$log2_fc_cutoff)
```

